Clear global environment and load libraries
```{r}
rm(list=ls())
library(CellChat)
library(patchwork)
library(dplyr)
library(Seurat)
options(stringsAsFactors = FALSE)
seurats <- c()
names <- c()
chats <- c()
chat_names <- c()
```

Read in Sequencing Matrix
```{r}
file_names <- c("LCMA01_BEVR_CD31", "LCMA04_GBM_CD31", "LCMA05_BEVR_Unsorted", "LCMA06_GBM_Unsorted", "LCMA11_BEVR_unpaired")
positions <- c(1, 2, 3, 4, 5)

duplicate <- FALSE

for (i in 1:length(file_names)){
  file_name <- file_names[i]
  for (name in names){
    if (file_name == name){
      duplicate <- TRUE
    }
  }
  if (duplicate) {
    duplicate <- FALSE
    next
  } else {
    names <- append(names, file_name)
  }
  position <- positions[i]
  directory_string <- paste("C:/Users/19193/OneDrive - The University of Chicago",
                            "/Documents/UChicago/Internships etc/",
                            "Internship Opportunities/Aghi Lab/CD31 sorted/",
                            file_name, "/filtered_feature_bc_matrix/",
                            sep = "")
  
  
  MTX <- ReadMtx(
    mtx = paste(directory_string, "matrix.mtx.gz", sep = ""),
    features = paste(directory_string, "features.tsv.gz", sep = ""),
    cells = paste(directory_string, "barcodes.tsv.gz", sep = ""))
  
  seurat <- CreateSeuratObject(counts = MTX)
  seurat <- subset(seurat, subset = nFeature_RNA > 200 & nFeature_RNA < 2500)
  attributes(seurat)$name <- file_name
  seurats <- append(seurats, seurat, position)
}

```

Seurat Data Prep
```{r}

for (i in 1:length(seurats)){
  seurats[[i]] <- NormalizeData(seurats[[i]], normalization.method = "LogNormalize", scale.factor = 10000)
  seurats[[i]] <- FindVariableFeatures(seurats[[i]], selection.method = "vst", nfeatures=2000)
  all_genes <- rownames(seurats[[i]])
  seurats[[i]]  <- ScaleData(seurats[[i]], features = all_genes, block.size = 1000)
}

# LCMA01_BEVR_CD31 <- subset(LCMA01_BEVR_CD31, subset= nFeature_RNA > 200 & nFeature_RNA < 2500)
# 
# LCMA01_BEVR_CD31 <- NormalizeData(LCMA01_BEVR_CD31, normalization.method = "LogNormalize", scale.factor = 10000)
# 
# LCMA01_BEVR_CD31 <- FindVariableFeatures(LCMA01_BEVR_CD31, selection.method = "vst", nfeatures=2000)
# 
# all.genes <- rownames(LCMA01_BEVR_CD31)
# 
# LCMA01_BEVR_CD31 <- ScaleData(LCMA01_BEVR_CD31, features = all.genes, block.size = 1000)
```
Create Clusters
```{r}
for (i in 1:length(seurats)){
  seurats[[i]] <- RunPCA(seurats[[i]],  features=VariableFeatures(object=seurats[[i]]))
  print(seurats[[i]][["pca"]], dims=1:15, nfeatures = 15)

  seurats[[i]] <- FindNeighbors(seurats[[i]], dims=1:10)
  seurats[[i]] <- FindClusters(seurats[[i]], resolution=0.5)

  seurats[[i]] <- RunUMAP(seurats[[i]], dims=1:10)
  DimPlot(seurats[[i]], reduction="umap")
}
```

Create Cell Chats
```{r}
#Identify Cluster Markers

# for (i in 1:length(seurats)){
#   seurat <- seurats[[i]]
#   for(j in 1:length(seurat@meta.data$seurat_clusters)){
#     markerName <- paste("marker", as.character(i), as.character(j), sep="")
#     assign(markerName, FindMarkers(LCMA01_BEVR_CD31, ident.1=j-1, min.pct=0.1))
#   }
# }

for (i in 1:length(seurats)){
  #Assign New Cluster Names
  vals <- as.numeric(as.character(seurats[[i]]$seurat_clusters))
  if (min(vals) == 0){
    seurats[[i]]$seurat_clusters <- as.factor(vals + 1)
  } else {
    while(min(vals) > 1){
      vals <- as.numeric(as.character(seurats[[i]]$seurat_clusters))
      seurats[[i]]$seurat_clusters <- as.factor(vals - 1)
    }
  }
  #Make Cell Chat Object
  chat_name <- attributes(seurats[[i]])$name
  for (c_name in chat_names){
    if (c_name == chat_name){
      duplicate <- TRUE
    }
  }
  if (duplicate) {
    duplicate <- FALSE
    print("test")
    next
  } else {
    chat_names <- append(chat_names, chat_name)
  }
  chats <- append(chats, createCellChat(object = seurats[[i]], group.by="seurat_clusters"))
}
MergedChat <- mergeCellChat(chats, file_names, cell.prefix=TRUE)
chats <- append(chats, MergedChat)
```

Set Database to Use
```{r}


"Set ligand-receptor interaction db"
CellChatDB <- CellChatDB.human
showDatabaseCategory(CellChatDB)
dplyr::glimpse(CellChatDB$interaction)

# use a subset of CellChatDB for cell-cell communication analysis
# CellChatDB.use <- subsetDB(CellChatDB, search = "Secreted Signaling") # use Secreted Signaling
# use all CellChatDB for cell-cell communication analysis
CellChatDB.use <- CellChatDB # simply use the default CellChatDB

# set the used database in the object
for (i in 1:length(chats)){
  chats[[i]]@DB <- CellChatDB.use
}
```


Calculate Relative Expression
```{r}
# subset the expression data of signaling genes for saving computation cost
for (i in 1:length(chats)){
  chats[[i]]@DB <- CellChatDB.use
  chats[[i]] <- subsetData(chats[[i]]) # This step is necessary even if using the whole database
  chats[[i]] <- identifyOverExpressedGenes(chats[[i]])
  chats[[i]] <- identifyOverExpressedInteractions(chats[[i]])
  
  # project gene expression data onto PPI (Optional: when running it, USER should set `raw.use = FALSE` in the function `computeCommunProb()` in order to use the projected data)

  # chats[[i]] <- projectData(chats[[i]], PPI.human)
}




```

Compute Probability that Two Cell Classes Communicate

WARNING: COMPUTATIONALLY EXPENSIVE!!! 
```{r}
future::plan("multisession", workers=4)
for (i in 1:length(chats)){
  chats[[i]] <- computeCommunProb(chats[[i]])
  # Filter out the cell-cell communication if there are only few number of cells in certain cell groups
  chats[[i]] <- filterCommunication(chats[[i]], min.cells = 10)
}
```

Generate Data Frames Containing Communication Networks
```{r}
i = 1
net_DF <- subsetCommunication(chats[[i]])
netP_DF <- subsetCommunication(chats[[i]], slot.name = "netP")
```

Compute Probability that Two Cell Classes Communicate, Organized by Pathway
```{r}
for (i in 1:length(chats)){
  chats[[i]] <- computeCommunProbPathway(chats[[i]])
}
```

Add Communication Network to CellChat Object, Overall and Pathway Specific
```{r}
#Generate interaction network
for (i in 1:length(chats)){
  chats[[i]] <- aggregateNet(chats[[i]])
}

#Visualize interaction network
# groupSize <- as.numeric(table(LCMA01_BEVR_CD31_Chat@idents))
# par(mfrow = c(1,2), xpd=TRUE)
# netVisual_circle(LCMA01_BEVR_CD31_Chat@net$count, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Number of interactions")
# netVisual_circle(LCMA01_BEVR_CD31_Chat@net$weight, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Interaction weights/strength")
```

Generate Circle Plots of Most Highly Expressed Pathways
```{r}
#Generate Circle Plots
for (i in 1:length(chats)){
  chats[[i]] <- netAnalysis_computeCentrality(chats[[i]], slot.name = "netP")
  par(mfrow=c(5,5))
  par(mai=c(0.1, 0.1, 0.1, 0.1))
  for (pathway in chats[[i]]@netP$pathways){
    print(pathway)
    netVisual_circle(chats[[i]]@netP$prob[,,pathway], title.name = pathway)
  }
}
```

```{r}
for (i in 1:length(chats)){
  len <- length(unique(chats[[i]]@meta$seurat_clusters))
  print(len)
  show(netVisual_bubble(chats[[i]], sources.use = c(1:len), targets.use = c(1:len), remove.isolate = FALSE))
}
```

Merge CellChats
```{r}
MergedChats <- mergeCellChat(chats, file_names, cell.prefix=TRUE)
```

```{r}
rankNet(MergedChats, mode="comparison", measure="weight", sources.use=c(1,2), targets.use=c(1,2), )
```
